Complete Real-Time Liver Model including Glisson Capsule, Vascular Network and Parenchyma

### 2013-03-01 Doc/Miccai2013/miccai2013.tex
paper outline
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@539 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

The paper is organized as follows: \TODO{paper organization}.

@@

\TG{summary of following sections.}

>>>>

The paper is organized as follows: first we describe the proposed vascularized
liver model with capsule (Sec. 2); then we show the correct behaviour of the
model in context of local deformations and finally we analyze the influence of
the capsule on the global deformations of the liver and show that despite the
small thickness it plays an important role also in the global context.

@@
